R for Clinical Study Reports and Submission

### 2021-07-09 intro.Rmd
update part3 title

- Part 3, "Submission package in eCTD" provides general information in preparing submission package related to CSR in 
electronic Common Technical Document (eCTD). In this part, we assume readers are project lead of a clinical project 
with experience in R package development as well.

>>>>

- Part 3, "eCTD Submission package" provides general information in preparing submission package related to CSR in 
electronic Common Technical Document (eCTD). In this part, we assume readers are project lead of a clinical project 
with experience in R package development as well.
